The title

### 2017-01-16 analysis/paper/paper.Rmd
Figure 1

![Landscape around the middle part of the Irrawaddy River near Chauk. View from the Chinthaungma monastery towards the west side of the river.](C:/Users/Maria/Documents/PhD Wollongong/Myanmar/Chauk/chaukgeomorph/P6200093.JPG)

@@

Landform 2 (L2) can be distinguished by the scarcity of vegetation compared to the lower landform 3 (L3). Probably due to the very thin or absent soil layer on top pf the bedrock, only grass, shrubs and some scattered trees grow on L2. The terrain is severely incised and has a lot of gently rolling gullies and valleys.

>>>>

```{r LandscapeChauk, fig.cap="Landscape around the middle part of the Irrawaddy River near Chauk. View from the Chinthaungma monastery towards the west side of the river."}
knitr::include_graphics("../figures/Landscape_Chauk.JPG")
```

@@

Landform 2 (L2) can be distinguished by the scarcity of vegetation compared to the lower landform 3 (L3). Probably due to the very thin or absent soil layer on top of the bedrock, only grass, shrubs and some scattered trees grow on L2 (Figure \@ref(fig:LandscapeChauk)). The terrain is severely incised and has a lot of gently rolling gullies and valleys.
